### 2023-10-31 thesis/chapters/appendix/B-plan-of-work.tex
Revise plan of work

\begin{table}[h!]
\def\arraystretch{1.25}
\begin{tabular}{|l|p{12cm}|}
\hline
\textbf{Period} & \textbf{Work}                                                                                                                                                                                                                         \\ \hline
\nth{1} week         & Semester kickoff meeting with the supervisor and consultant to set goals, experiments and discuss status of collaborations with the industry.
\\ \hline
\nth{2} week         &  Arrange collaboration with alternative industry partner. Prepare checklist for technical inspection of machinery. Construct device for exploratory measurements.
\\ \hline
\nth{3} week         & Technical inspection of air conditioning units in data centre of the industry partner. Feature extraction: calculate features from Mafaulda dataset.
 \\ \hline
\nth{4} week         & Consultation with the supervisor about choice of machine to measure (scroll compressor), device for measurement, and requirements for dataset gathering. Fine tune measurement device.
 \\ \hline
\nth{5} week         &  Feature selection: create procedures to determine sets of best data features in Mafaulda dataset.
 \\ \hline
\nth{6} week         & Generate comprehensive reports from jupyter notebooks. Mafaulda feature sampling for kNN multiclass classification.
 \\ \hline
\nth{7} week         & ?Consultation with the supervisor ... Feed exporatory dataset into anomaly detection models.
 \\ \hline
 \nth{8} week         & 
 \\ \hline
 \nth{9} week         & ??Make further exploratory measurements with rewritten code ensuring more precise accelerometer sampling. Make a plan of measurement and negotiate it with industry partner.
 \\ \hline
  \nth{10} week         & ?Begin writing implementation
 \\ \hline
  \nth{11} week         & 
 \\ \hline
  \nth{12} week         & 
 \\ \hline
\end{tabular}
\end{table}

>>>>

\begin{table}[h!]
\def\arraystretch{1.25}
\begin{tabular}{|l|p{12cm}|}
\hline
\textbf{Period} & \textbf{Work}                                                                                                                                                                                                                         \\ \hline
\nth{1} week         & Semester kickoff meeting with the supervisor and consultant to set goals, experiments and discuss status of collaborations with the industry.
\\ \hline
\nth{2} week         &  Arrange collaboration with alternative industry partner. Prepare checklist for technical inspection of machinery. Construct device for exploratory measurements.
\\ \hline
\nth{3} week         & Technical inspection of air conditioning units in data centre of the industry partner. Feature extraction step to calculate features from Mafaulda dataset.
 \\ \hline
\nth{4} week         & Consultation with the supervisor about choice of machine to measure (scroll compressor), device for measurement, and requirements for dataset gathering. Fine tune measurement device.
 \\ \hline
\nth{5} week         &  In feature selection use various metrics to determine sets of best data features in Mafaulda dataset.
 \\ \hline
\nth{6} week         & Generate reports from jupyter notebooks. Feature sampling used in kNN multiclass and binary classificator.
 \\ \hline
\nth{7} week         & Explore streaming ML models with Mafaulda dataset. Consultation with the supervisor and status report.
 \\ \hline
 \nth{8} week         & ?Anomaly detection models evaluation and conclude/gather all the findings.
 \\ \hline
 \nth{9} week         & ??Make further exploratory measurements with rewritten code ensuring more precise accelerometer sampling. Make a plan of measurement and negotiate it with industry partner.
 \\ \hline
  \nth{10} week         & ?Begin writing implementation
 \\ \hline
  \nth{11} week         & 
 \\ \hline
  \nth{12} week         & 
 \\ \hline
\end{tabular}
\end{table}
